---
title: "Q & A"
author: "Isabella Hundley"
date: "October 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(scales)
```

## Q&A

There are 'r sum(enrolled$sectionSize)' students enrolled in the in-class sections of ISDS 1102 this semester.

### Submissions

How many students submit assignments per day?

```{r}
ggplot(dailySubs, aes(x=subDate, y = n)) + geom_col() + theme_minimal()
```

What percent of students have submitted assignments?
```{r}
ggplot(totalSubs, aes(x = label, y = pSub)) + geom_col() + theme_minimal() +
  scale_y_continuous(name = "", labels = percent) + theme(axis.text.x = element_text(angle=45, hjust=1))

ggplot(fullSubs, aes(x = label, y = pSub)) + geom_col() + facet_wrap(~sectionId) + theme_minimal() + 
  scale_y_continuous(name = "", labels = percent) + 
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

Of the students that have submitted an assignment, what percent submitted multiple times?
```{r}
ggplot(totalSubs, aes(x = label, y = pManySubs)) + geom_col() + theme_minimal() +
  scale_y_continuous(name = "", labels = percent) + theme(axis.text.x = element_text(angle=45, hjust=1))

ggplot(fullSubs, aes(x = label, y = pManySubs)) + geom_col() + facet_wrap(~sectionId) + theme_minimal() +
  scale_y_continuous(name = "", labels = percent) + 
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

How many students have not submitted any files (per chunk)?

```{r}

```




