---
title: "Q & A"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

library(scales)
library(knitr)

source('backEnd.R')
source('links.R')
```


There are `r sum(enrolled$sectionSize)` students enrolled in the in-class sections of ISDS 1102 this semester.

#### Submissions

How many students submit assignments per day?

```{r}
ggplot(dailySubs, aes(x=subDate, y = n)) + geom_col() + theme_minimal()
```

What percent of students have submitted assignments?
```{r}
ggplot(totalSubs, aes(x = label, y = pSub)) + geom_col() + theme_minimal() +
  scale_y_continuous(name = "", labels = percent) + theme(axis.text.x = element_text(angle=45, hjust=1))

ggplot(fullSubs, aes(x = label, y = pSub)) + geom_col() + facet_wrap(~sectionId) + theme_minimal() + 
  scale_y_continuous(name = "", labels = percent) + 
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

Of the students that have submitted an assignment, what percent submitted multiple times?
```{r}
ggplot(totalSubs, aes(x = label, y = pManySubs)) + geom_col() + theme_minimal() +
  scale_y_continuous(name = "", labels = percent) + theme(axis.text.x = element_text(angle=45, hjust=1))

ggplot(fullSubs, aes(x = label, y = pManySubs)) + geom_col() + facet_wrap(~sectionId) + theme_minimal() +
  scale_y_continuous(name = "", labels = percent) + 
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

How many students have not submitted any files (per chunk)?

```{r}
table = data.frame(chunk = c('a'), students = c(12), stringsAsFactors = FALSE)
inc <- 1
for (name in as.vector(cNames$label)){
  table[inc, 1] <- name
  table[inc, 2] <- length(badChunks[[name]])
  inc <- inc + 1
}

ggplot(table, aes(x = chunk, y = students)) + geom_col() + theme_minimal() + 
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

Students that have not submitted any files for e1a:
    `r badChunks$e1a`


#### Attendance
```{r}
attTable %>% ggplot(aes(x = eventDate, y = n)) + geom_col(aes(fill = eventTopic), position = 'dodge') +
  facet_wrap(~sectionId)
```


### Links

What students have clicked the links on the syllabus page?
`r kable(syllabusLinks)`

What pages are students clicking links from?
```{r}
topicLinks %>% filter(pageCategory == 'is') %>% group_by(date, topic) %>% 
  summarise(clicks = sum(clicks)) %>%
  ggplot(aes(x = date, y = clicks, color = topic)) + geom_line() + theme_minimal() +
  ggtitle('Information Systems', subtitle = 'Outbound Link Clicks by Date & Topic')
```

```{r}
topicLinks %>% filter(pageCategory == 'excel') %>% group_by(date, topic) %>% 
  summarise(clicks = sum(clicks)) %>%
  ggplot(aes(x = date, y = clicks, color = topic)) + geom_line() + theme_minimal() +
  ggtitle('Excel', subtitle = 'Outbound Link Clicks by Date & Topic')
```

```{r}
topicLinks %>% filter(pageCategory == 'word') %>% group_by(date, topic) %>% 
  summarise(clicks = sum(clicks)) %>%
  ggplot(aes(x = date, y = clicks, color = topic)) + geom_line() + theme_minimal() +
  ggtitle('Word', subtitle = 'Outbound Link Clicks by Date & Topic')
```


